|

### 2021-04-16 documentation/paper.Rmd
Recompiled pollbasepro

---
title: |
  | PollBasePro: Daily Estimates of Aggregate Voting Intention in Britain from `r format(min(britpol::pollbasepro$date), "%Y")` to the Present Day\thanks{This article benefitted from much useful feedback. We owe particular thanks Chris Hanretty, who inspired this project and provided much useful feedback. We would also like to thank Hannah Willis, Chris Wlezien, and Patrick English for offering their time to review our manuscript. Finally, we would like to extend a special thanks to all of the volunteers who work to maintain such a comprehensive list of British opinion polling data on Wikipedia.}
author: |
  | Jack Bailey\thanks{Research Associate, Department of Politics, University of Manchester, UK. If you have any comments or questions, feel free to contact me either by email (\href{mailto:jack.bailey@manchester.ac.uk}{jack.bailey@manchester.ac.uk}) or on Twitter (\href{https://www.twitter.com/PoliSciJack}{@PoliSciJack}).}, Mark Pack\thanks{President, The Liberal Democrats, UK}, & Luke Mansillo\thanks{PhD Candidate, Department of Government \& International Relations, University of Sydney, Australia}
date: |
  | \small This version compiled `r stringr::str_remove(format(Sys.time(), '%d %B %Y'), "^0")` using PollBasePro `r paste0("v", packageVersion("britpol"))`
abstract: |
  | Political scientists often use public opinion polls to test their theories. Yet these data present some difficulties. First, they are noisy. Second, they occur at irregular intervals. Third, they measure both public preferences and pollsters' survey design choices. We introduce a new dataset, PollBasePro, that accounts for these issues. It includes voting intention estimates for each of Britain's three largest parties on each day between the 1955 general election and the present. As the dataset covers `r format(nrow(britpol::pollbasepro), big.mark = ",")` days in total, it is perhaps more comprehensive than any other existing time series of British political opinion. We then use our estimates to test a question of pressing importance: how daily deaths attributable to COVID-19 have influenced support for the governing Conservative Party.
  |
  | \textbf{\textsf{Keywords:}} Opinion polls; public opinion; British politics; Bayesian methods.
indent: yes
fontsize: 12pt
geometry: margin = 1.15in
subparagraph: yes
compact-title: false
bibliography: _assets/master.bib
biblio-style: _assets/apsr.bst
classoption: a4paper
linkcolor: black
urlcolor: violet
citecolor: black
output: 
  bookdown::pdf_document2: 
    latex_engine: xelatex
    toc: false
    keep_tex: false
    includes:
      in_header:
        - _assets/rmd-preamble.tex
    number_sections: false
    fig_caption: true
---

@@

As well as summarising facts about the parties, our estimates also allow us to make general claims about the relationships that exist *between* the parties. As figure \@ref(fig:cor-plot) shows, these are all negative. Consider the effect of rising Liberal support on the Conservatives and Labour. The correlation between the Liberals and the Conservatives is `r britpol:::in_text(cor_mods$lib_con*100, suffix = "%", inside = F)` and between the Liberals and Labour `r britpol:::in_text(cor_mods$lib_lab*100, suffix = "%", inside = F)`. Contrary to popular arguments that the Liberals serve to split the centre-left vote [e.g. @jenkins2019], our figures suggest that rising Liberal support has tended to hurt the Conservatives more than Labour. Interestingly, the correlation between Labour and the Conservatives is also the smallest, at `r britpol:::in_text(cor_mods$con_lab*100, suffix = "%", inside = F)`. This is perhaps unsurprising, given that the two parties represent different sides of the left-right spectrum. Even so, that both parties have tended to target the other's vote still makes strategic sense: each party's pool of potential voters is almost always larger than the pool of potential Liberal voters.

@@

At present, all values of $\alpha_{Day}$ are independent. This is a problem. First, we want estimates closer together to be more similar. Second, some days have no polling data to inform them. To address this problem, we constrain $\alpha_{1}$ to be equal to the vote share that a given party received at a given election. We also constrain $\alpha_{T}$ to be equal to the vote share that the same party received at the following election. Next, we fit a dynamic model to $\alpha_{t}$ for all days in our time series except for the first and last. This acts as a sort of "chain" that links together all values of $\alpha$. Because these values are now linked, they can then share information amongst themselves. This means that when the value of one estimate changes during the model estimation process, so too do the values of all others. The model assumes that $\alpha_{t}$ is equal to $\alpha_{t-1}$, plus any random shocks that take place between the two days, $\omega_{t-1}$. These random shock parameters are themselves scaled according to $\tau$, the scale of innovations parameter. Updating our model specification again, we get:

>>>>

---
title: |
  | PollBasePro: Daily Estimates of Aggregate Voting Intention in Britain from `r format(min(britpol::pollbasepro$date), "%Y")` to the Present Day\thanks{This article benefitted from much useful feedback. We owe particular thanks Chris Hanretty, who inspired this project and provided much useful feedback. We would also like to thank Hannah Willis, Chris Wlezien, and Patrick English for offering their time to review our manuscript. Finally, we would like to extend a special thanks to all of the volunteers who work to maintain such a comprehensive list of British opinion polling data on Wikipedia.}
author: |
  | Jack Bailey\thanks{Research Associate, Department of Politics, University of Manchester, UK. If you have any comments or questions, feel free to contact me either by email (\href{mailto:jack.bailey@manchester.ac.uk}{jack.bailey@manchester.ac.uk}) or on Twitter (\href{https://www.twitter.com/PoliSciJack}{@PoliSciJack}).}, Mark Pack\thanks{President, The Liberal Democrats, UK}, & Luke Mansillo\thanks{PhD Candidate, Department of Government \& International Relations, University of Sydney, Australia}
date: |
  | \small This version compiled `r stringr::str_remove(format(Sys.time(), '%d %B %Y'), "^0")` using PollBasePro `r paste0("v", packageVersion("britpol"))`
abstract: |
  | Political scientists often use public opinion polls to test their theories. Yet these data present some difficulties. First, they are noisy. Second, they occur at irregular intervals. Third, they measure both public preferences and pollsters' survey design choices. We introduce a new dataset, PollBasePro, that accounts for these issues. It includes voting intention estimates for each of Britain's three largest parties on each day between the 1955 general election and the present. As the dataset covers `r format(nrow(britpol::pollbasepro), big.mark = ",")` days in total, it is perhaps more comprehensive than any other existing time series of British political opinion. We then use our estimates to test a question of pressing importance: how daily deaths attributable to COVID-19 have influenced support for the governing Conservative Party.
  |
  | \textbf{\textsf{Keywords:}} Opinion polls; public opinion; British politics; Coronavirus; COVID-19; Bayesian methods.
indent: yes
fontsize: 12pt
geometry: margin = 1.15in
subparagraph: yes
compact-title: false
bibliography: _assets/master.bib
biblio-style: _assets/apsr.bst
classoption: a4paper
linkcolor: black
urlcolor: violet
citecolor: black
output: 
  bookdown::pdf_document2: 
    latex_engine: xelatex
    toc: false
    keep_tex: false
    includes:
      in_header:
        - _assets/rmd-preamble.tex
    number_sections: false
    fig_caption: true
---

@@

As well as summarising facts about the parties, our estimates also allow us to make general claims about the relationships that exist *between* the parties. As figure \@ref(fig:cor-plot) shows, these are all negative. Consider the effect of rising Liberal support on the Conservatives and Labour. The correlation between the Liberals and the Conservatives is strong at `r britpol:::in_text(cor_mods$lib_con*100, suffix = "%", inside = F)` and between the Liberals and Labour `r britpol:::in_text(cor_mods$lib_lab*100, suffix = "%", inside = F)`. Contrary to popular arguments that the Liberals serve to split the centre-left vote [e.g. @jenkins2019], our figures suggest that rising Liberal support has tended to hurt the Conservatives more than Labour. The correlation between Labour and the Conservatives is also sizeable, at `r britpol:::in_text(cor_mods$con_lab*100, suffix = "%", inside = F)`. Given that they are Britain's two main parties, this is perhaps unsurprising: Labour and the Conservatives are the only parties likely to form a government after any election and punishing one often requires voting for the other.

@@

At present, all values of $\alpha_{Day}$ are independent. This is a problem. First, we want estimates closer together to be more similar. Second, some days have no polling data to inform them. To address this problem, we constrain $\alpha_{1}$ to be equal to the vote share that a given party received at a given election. We also constrain $\alpha_{T}$ to be equal to the vote share that the same party received at the following election. Next, we fit a dynamic model to $\alpha_{t}$ for all days in our time series except for the first and last. This acts as a sort of "chain" that links together all values of $\alpha$. Because these values are now linked, they can then share information amongst themselves. This means that when the value of one estimate changes during the model estimation process, so too do the values of all others. The model assumes that $\alpha_{t}$ is equal to $\alpha_{t-1}$, plus any random shocks that take place between the two days, $\omega_{t-1}$. These random shock parameters are themselves scaled according to $\tau$, the scale of innovations parameter. Updating the model again, we get:
